---
title: "Chapter 5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gapminder)
library(here)
library(socviz)
library(tidyverse)
theme_set(theme_bw())
```


Objects passed along the pipeline and the functions acting on them carry some assumptions about their context.
  - Don’t have to keep specifying the name of the underlying data frame object you are working from. Everything is implicitly carried forward from gss_sm.
  - Within the pipeline, the transient or implicit objects created from your summaries and other transformations are carried through, too.
```{r echo=FALSE}
rel_by_region <- gss_sm %>%
  group_by(bigregion, religion) %>%
  summarize(count = n()) %>%
  mutate(freq = count / sum(count), pct = round(freq * 100, 0)) %>%
  drop_na(religion)

p <- ggplot(rel_by_region, aes(x = bigregion, y = pct, fill = religion))
p + geom_col(position = "dodge2") +
  labs(x = NULL, y = 'Percent', fill = "Religion") +
  guides(fill = FALSE) +
  coord_flip() +
  facet_grid( ~ bigregion)
### THE ABOVE PRODUCES THE WRONG PLOT because 'x' is still 'bigregion' and we don't need that since 'facet_wrap()' will seperate the charts for us by 'bigregion'
### 

p <- ggplot(rel_by_region, aes(x = religion, y = pct, fill = religion))
p + geom_col(position = "dodge2") +
  labs(x = NULL, y = 'Percent', fill = "Religion") +
  guides(fill = FALSE) +
  coord_flip() +
  facet_grid( ~ bigregion)
```

## ORGAN DATASET
```{r}
# organdata %>% select(1:6) %>% slice_sample(n = 10)
p = ggplot(organdata, aes(reorder(country, donors, na.rm=TRUE), donors, fill=world))
p + geom_boxplot() +
  coord_flip()
  
```

```{r}
# Plotting the points like this leads to overplotting in many cases.
p = ggplot(organdata, aes(reorder(country, donors, na.rm=TRUE), donors, color=world))
p + geom_point() +
  coord_flip()
# May use geom_jitter to scatter the points a little bit to get a better idea of the data
# The default jitter is too much so decrease it jitter
p + geom_jitter(position=position_jitter(width = 0.15))+
  coord_flip()
```

### Ceveland Dot Plots
```{r}
# LOTS OF REDUNDANT CODE. There is a better way to do this
# by_country <- organdata %>% group_by(consent_law, country) %>%
#   summarize(
#     donors_mean = mean(donors, na.rm = TRUE),
#     donors_sd = sd(donors, na.rm = TRUE),
#     gdp_mean = mean(gdp, na.rm = TRUE),
#     health_mean = mean(health, na.rm = TRUE),
#     roads_mean = mean(roads, na.rm = TRUE),
#     cerebvas_mean = mean(cerebvas, na.rm = TRUE)
#   )

by_country = organdata %>% group_by(consent_law, country) %>%
  summarize_if(is.numeric, funs(mean, sd), na.rm = TRUE) %>%
  ungroup()

p = ggplot(by_country, aes(x = reorder(country, donors_mean),
                           y = donors_mean,
                           color = consent_law))
p + geom_pointrange(aes(ymin = donors_mean - donors_sd,
                        ymax = donors_mean + donors_sd)) +
  coord_flip() +
  facet_wrap(~ consent_law, ncol = 1, scales = 'free_y')
# WHEN ONE AXIS IS CATEGORICAL, can allow it to SCALE FREELY when using multiple facets
```

